% Senior thesis or Junior Project Acknowledgements  -----------------------------------------------------

Thank you to my thesis adviser Prof.~Laure Resplandy who has helped me think through my research questions, understand atmospheric processes, and for her support and patience in helping me with the direction this project has taken.
Thank you to my Junior Paper adviser and second reader Prof.~Frederik J.~Simons who helped me with
the conceptualization, direction, and revision of earlier portions of this project. Frederik's excitement about research and support of undergrads trying to wrap their heads around complex ideas has been a major reason why I chose to concentrate in Geosciences. Thank you to the second reader of my Fall Junior Paper, Prof.~Jessica Irving for feedback, suggestions, and encouragement. Thanks to Dr.~Amanda
Irwin Wilkins and ``The Hare'' writing workshop group for discussing
and editing various figures and drafts of my Junior Papers and for being a wonderful group of creative, curious, and competent people who give excellent feedback and support and fed me dinner. Thank you to Prof.~Adam C.~Maloof who taught me \LaTeX and for the past three years has provided an omnipresent voice in my head asking me if I was ``changing the world'' which has been both a source of inspiration and stress. Thanks to Dr.~Chris Harig at the University of Arizona for providing some of the data files for my Fall Junior Paper. Thank you to Prof.~Gabriel Vecchi for helpful insights into atmospheric and oceanic processes. Thank you to the numerous professors and graduate and undergraduate students in the Princeton Department of Geosciences for feedback, encouragement, and constructive criticism on various presentations of preliminary results. Thank you to all of my friends and family who read drafts of various independent work and provided helpful feedback. Lastly, an especially big thanks to all of the people who asked me, ``What is your independent work about?'' and then patiently listened while I struggled to articulate my project in a way that made any sense.

My Mom and Dad have always encouraged me to pursue my interests, and their support has opened up so many life-changing opportunities for me. Finally, thank you to Drew Brazer for making sure that I never missed room draw or course registration these past three years, and for reading sections of this paper.

