\documentclass [11pt]{article}
\widowpenalty=10000 
\clubpenalty=10000 
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{wasysym}
\usepackage{graphicx}
\usepackage{pslatex}
\usepackage{lscape}
\usepackage{rotating}
\usepackage[T1]{fontenc}
\usepackage[latin1]{inputenc}
\usepackage{longtable}
\usepackage[font=scriptsize,labelfont=bf]{caption}
\setlength{\LTcapwidth}{5.5 in}
\usepackage{url}
\usepackage{lastpage}
\usepackage{lineno}
\usepackage[english]{babel}
\usepackage[usenames, dvipsnames]{color}
\usepackage[round, sort, numbers, authoryear]{natbib}
\usepackage{hyperref}
%\usepackage{soul}
\usepackage{csquotes}
\usepackage{bibentry}
\usepackage{xcolor}
\usepackage{fancyhdr}
\nobibliography*

% Now setup margins and linespacing
\textwidth = 6.5 in
\textheight = 8.84 in
\addtolength{\voffset}{-0.04in} 
\oddsidemargin = 0.0 in
\evensidemargin = 0.0 in
\topmargin =  0.0 in
\headheight = 0.1 in
\headwidth = 6.5 in
\headsep = 0.25 in
\parskip = 0.1 in
\parindent = 0.3 in
\linespread{1.25}


\newcommand{\entry}[2]{\hl{\cite{#1}}\\\\ \indent\indent #2}

\newcommand{\hl}[1]{\colorbox{yellow}{\textcolor{red}{#1}}}


\title{Annotated Bibliography}
\author{Benjamin Getraer\\Princeton University}

\begin{document}
\maketitle

\entry{mattingly2018}{Detailed analyses of Atmospheric River impacts partitioned by season, area of intersection with Greenland Ice Sheet, and strength of moisture transport. Self-Organizing Map classification and conventional object-based Atmospheric River identification algorithm to identify moisture transport events.

Data: 
\begin{enumerate}
\item ``integrated vapor transport'' data from MERRA-2 atmospheric reanalysis dataset, 1980--2016.
\item MAR 3.8 climate model (total melt, snowfall, surface mass balance, surface temperature).
\item National Snow and Ice Center MEaSUREs Greenland surface melt daily dataset, 1979--2015.
\end{enumerate}

Results:
\begin{enumerate}
\item AR in different locations associated with different NAO phases.
\item Change in AR locations between 2000--2009, 2010--2012, 2013--2016.
\item Different effects depending on W vs E AR.
\end{enumerate}
Discussion:
\begin{enumerate}
\item Relation to NAO, blocking, extratropical cyclones, Rossby wave breaking.
\item Uncertain relation to cloud cover per se.
\end{enumerate}
}

\entry{mattingly2018}


\bibliographystyle{/Users/benjamingetraer/Documents/IndependentWork/LatexFiles/gji}
\bibliography{/Users/benjamingetraer/Documents/IndependentWork/LatexFiles/bgetraerBib}
\end{document}